Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-27 paper.tex
update

\title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
 \author{Chen Wang, Hui Ma, Aaron Chen\\ School of
 Engineering and Computer Science, Victoria University of Wellington, New Zealand\\
Email: chen.wang@ecs.vuw.ac.nz, hui.ma@ecs.vuw.ac.nz, aaron.chen@ecs.vuw.ac.nz}

@@

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers (semantic matchmaking and QoS optimisation). Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirement of service users. E.g., minimum cost, maximal reliability. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are few works concerns both quality of semantic matchmaking and quality of services at the same time and points out the benefits clearly. Therefore, In this paper, we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition and present an automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement.  The results show our method can find better semantic matchmaking quality with a very slight trade off in QoS. Also, our method performs better in finding optimised solution with a trade off in execution time comparing an existing GP-based method.

@@

\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. Due to the increase of the number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition enjoys less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge $(1)$ in syntactic and semantics dimensions. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantics aspect, on the other hand, demands further research. Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other. There are many ontologies languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$). This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements (SLA) \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition focus mainly on addressing the one of challenges above. A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach. Meanwhile, many research works consider the possibility of generating a composite plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously. To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking. Therefore, a comprehensive quality model is needed to be addressed, and more methods are needed to be applied specifically on the problem that optimises semantic matchmaking quality and QoS simultaneously.

The overall goal of this paper is to \textit{develop an comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matching optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solution \cite{da2016particle}, we will propose a PSO-based service composition approach using our comprehensive quality model, which is also considered to be more applicable way to measure semantic matchmaking in automated semantic web service composition. We will achieve three objectives in this work as follows:

\begin{enumerate}
 \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarity. This method is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.

@@

 \item To evaluate the performance of comprehensive quality awareness semantic web service composition by utilising benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}. Also, we make a comparison between PSO-based and an existing GP-based approach employing our proposed comprehensive quality model.

@@

Gupta et al. \cite{gupta2015optimization} proposed an improved Genetic Algorithm for QoS-ware web service composition, where some population associated with lower fitness are discarded with bringing in new offerings in each generation. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation. A hyper approach employs both a greedy search algorithm and genetic programming is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to generate directed acrylic graph as composite solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process. A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation.

Other non-EC techniques are also introduced in QoS-ware web service composition. A heuristic service composition method is proposed by Tang et al. \cite{qi2010combining} proposed,  named local optimisation and enumeration, which is to filter a small number of promising candidates related to each task by local selection, and all the composite solutions are enumerated to reach the near-to-optimal.

However, composite solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two solutions employing different evaluation model in Sect. \ref{comparisonTest}. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and parameter-related concept similarity to determine the overall quality of web service composition. Also, Weighed graphs are utilised as representationd of semantic web service composition decoded from optimised service queue using PSO adopted from \cite{da2016particle}.
\section{Problem Description}\label{problemDes}

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part focus on transfering a given task input or input set to the desired Task output or output set. It typically refers to users' functional requirement. Another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. If no atomic web service could satisfy the composite goal, a combination of web services will be found to meet $Comp.G$. To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.

@@

\begin{itemize}
\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ S_{output} \in S_{1} \equiv S_{input}S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($S_{output} \in S_{1} \sqsubseteq_{n} S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($S_{output} \in S_{1} \sqsupseteq_{n} S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
\item \textit{Fail} ($\perp$). Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($S_{output} \in S_{1} \perp S_{input} \in S_{2}$), if none of the previous matches discovered.
\end{itemize}
\vspace{-0.5cm}
\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS, which covers aspects in non-functional requirements. This problem has been explored in both single objective and multi-objectives optimisation problems. Customers prefer lowest execution cost with highest response time and reliability that could be optimised simultaneously. According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}. Here we consider two composite constructs: sequence and parallel constructs, in building the composite web service. The QoS calculation models are described as follows:

\begin{figure}[h]
\centerline{
\fbox{
\begin{tabular}{p{0.6\linewidth}}
\space\hfill\includegraphics[width=2in]{sequence.pdf}\hfill\space\\[0.2cm]
$T=\sum\limits^m_{n=1}t_n$ \hfill $C=\sum\limits^m_{n=1}c_n$ \hfill
$A=\prod\limits^m_{n=1}a_n$ \hfill $R=\prod\limits^m_{n=1}r_n$
\end{tabular}}}
\caption{Sequence construct and calculation of its QoS properties
\cite{yu2013adaptive}.}
\label{sequence}
%\end{figure}
\vspace{0.3cm}
%\begin{figure}
\centerline{
\fbox{
\begin{tabular}{p{0.6\linewidth}}
\space\hfill\includegraphics[width=1.4in]{parallel.pdf}\hfill\space\\[0.2cm]
\space\hfill$T=MAX\{t_n|n\in\{1,\ldots,m\}\}$\hfill\space\\[0.2cm]
$C=\sum\limits^m_{n=1}c_n$ \hfill $A=\prod\limits^m_{n=1}a_n$ \hfill
$R=\prod\limits^m_{n=1}r_n$
\end{tabular}}}
\caption{Parallel construct and calculation of its QoS properties
\cite{yu2013adaptive}.}
\label{parallel}
\end{figure}
\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Fig. \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed concurrently. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composite flow of the solution. This construct is presented in Fig. \ref{parallel}.

@@

In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both semantic matchmaking quality and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 4. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation.

@@

\textbf{Quality aggregate matrix}. The quality aggregation is defined based on the constructs of composite web services, in consideration of functional and non-functional properties. The quality on construct level is further calculated by following the rules summarised in Table \ref{table1}.

@@

\subsection{Composition Weighted Graph}
We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which is described in Fig. \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$ assigned as weights.

@@

Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in composite web services obtained through two different methods. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the two optmised solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different. We make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertices in terms of quality of semantic matchmaking and QoS attributes in Fig. \ref{comparisontest} $(3)$. We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off. To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in Fig. \ref{comparisontest} $(4)$. $Ser1640238160$ and $Ser1947554374$ are selected service vertices with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter related to concept $Con2113572083$. There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$. It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality.

>>>>

\title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
\author{Chen Wang, Hui Ma, Aaron Chen\\ \small School of
Engineering and Computer Science, Victoria University of Wellington, New Zealand\\
Email: \{chen.wang, hui.ma, aaron.chen\}@ecs.vuw.ac.nz}

@@

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and QoS optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirement of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are few works concerns both quality of semantic matchmaking and QoS at the same time and points out the benefits clearly. Therefore, In this paper, proposed a more comprehensive quality model which is suitable to be tackled through EC algorithms and developed a general EC-based service composition system with explicit support for the comprehensive model, which can generate service composition solutions that meet both functional and non-functional requirement. We have evaluate our proposed model by comparing QoS evaluation model using benchmark dataset. The results show our approach can produce more opimised semantic matchmaking quality with a very slight trade off in QoS. We also conduct a experiment shows our EC mehtod performs better in finding more optimised solution by comparing one existing GP-based method using our proposed model.

@@

\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composition service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. Due to the increase of the number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition enjoys less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge $(1)$ in syntactic and semantics dimensions. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantics aspect, on the other hand, demands further research. Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other. There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$). This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements (SLA) \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition focus mainly on addressing the one of challenges above. A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach \cite{parejo2008qos,bahadori2009optimal}. Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously. To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking.

The overall goal of this paper is to \textit{develop an comprehensive appraoch to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach using our comprehensive quality model to measure semantic matchmaking in automated semantic web service composition. We will achieve three objectives in this work as follows:

\begin{enumerate}
 \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarity.

@@

 \item To evaluate our proposed approach, we conduct experiment to compare our comphensive quality model with QoS evaluation model, we also compare an one existing GP approach with our appraoch using our comprehensive model. Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

@@

Gupta et al. \cite{gupta2015optimization} proposed an improved Genetic Algorithm for QoS-ware web service composition, where some population associated with lower fitness are discarded with bringing in new offerings in each generation. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation. A hyper approach employs both a greedy search algorithm and genetic programming is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process. A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as composition solution in their PSO algorithm considering QoS optimisation.

Other non-EC techniques are also introduced in QoS-ware web service composition. A heuristic service composition method is proposed by Tang et al. \cite{qi2010combining} proposed,  named local optimisation and enumeration, which is to filter a small number of promising candidates related to each task by local selection, and all the composition solutions are enumerated to reach the near-to-optimal.

However, composition solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two solutions employing different evaluation model in Sect. \ref{comparisonTest}. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and parameter-related concept similarity to determine the overall quality of web service composition. Also, Weighed graphs are utilised as representationd of semantic web service composition decoded from optimised service queue using PSO adopted from \cite{da2016particle}.
\section{Problem Description}\label{problemDes}

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composition goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composition goal is demonstrated in two parts. The first functional part focus on transfering a given task input or input set to the desired Task output or output set. It typically refers to users' functional requirement. Another nonfunctional part specifies the acceptable level of composition quality of service. To accomplish the composition goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. If no atomic web service could satisfy the composition goal, a combination of web services will be found to meet $Comp.G$. To ensure the composition solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.

@@

\begin{itemize}
\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ S_{output} \in S_{1} \equiv S_{input}S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($S_{output} \in S_{1} \sqsubseteq_{n} S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($S_{output} \in S_{1} \sqsupseteq_{n} S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
\item \textit{Fail} ($\perp$). Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($S_{output} \in S_{1} \perp S_{input} \in S_{2}$), if none of the previous matches discovered.
\end{itemize}
\vspace{-0.5cm}
\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS, which covers aspects in non-functional requirements. This problem has been explored in both single objective and multi-objectives optimisation problems. Customers prefer lowest execution cost with highest response time and reliability that could be optimised simultaneously. According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}. Here we consider two composition constructs: sequence and parallel constructs, in building the composition web service. The QoS calculation models are described as follows:

\begin{figure}[h]
\centerline{
\fbox{
\begin{tabular}{p{0.6\linewidth}}
\space\hfill\includegraphics[width=2in]{sequence.pdf}\hfill\space\\[0.2cm]
$T=\sum\limits^m_{n=1}t_n$ \hfill $C=\sum\limits^m_{n=1}c_n$ \hfill
$A=\prod\limits^m_{n=1}a_n$ \hfill $R=\prod\limits^m_{n=1}r_n$
\end{tabular}}}
\caption{Sequence construct and calculation of its QoS properties
\cite{yu2013adaptive}.}
\label{sequence}
%\end{figure}
\vspace{0.3cm}
%\begin{figure}
\centerline{
\fbox{
\begin{tabular}{p{0.6\linewidth}}
\space\hfill\includegraphics[width=1.4in]{parallel.pdf}\hfill\space\\[0.2cm]
\space\hfill$T=MAX\{t_n|n\in\{1,\ldots,m\}\}$\hfill\space\\[0.2cm]
$C=\sum\limits^m_{n=1}c_n$ \hfill $A=\prod\limits^m_{n=1}a_n$ \hfill
$R=\prod\limits^m_{n=1}r_n$
\end{tabular}}}
\caption{Parallel construct and calculation of its QoS properties
\cite{yu2013adaptive}.}
\label{parallel}
\end{figure}
\subsubsection{Sequence construct}
The composition web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Fig. \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed concurrently. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composition flow of the solution. This construct is presented in Fig. \ref{parallel}.

@@

In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both semantic matchmaking quality and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 4. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation.

@@

\textbf{Quality aggregate matrix}. The quality aggregation is defined based on the constructs of composition web services, in consideration of functional and non-functional properties. The quality on construct level is further calculated by following the rules summarised in Table \ref{table1}.

@@

\subsection{Composition Weighted Graph}
We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which is described in Fig. \ref{wscs}. The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$ assigned as weights.

@@

Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in web services composition obtained through two different methods. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the two optmised solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different. We make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertices in terms of quality of semantic matchmaking and QoS attributes in Fig. \ref{comparisontest} $(3)$. We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off. To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in Fig. \ref{comparisontest} $(4)$. $Ser1640238160$ and $Ser1947554374$ are selected service vertices with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter related to concept $Con2113572083$. There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$. It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality.
